### 2016-11-18 src/local.tex
going to think

In this section we consider the unweighted variants of the problem.
We describe and analyze a local search algorithm, 
and show that when the maximum possible capacity, $C$, is fixed, the algorithm achieves 
a $\frac{C + 1}{2C}$ approximation ratio.
Throughout this section we consider $C$ to be fixed, and $k$ to be a fixed parameter.

@@

\begin{algorithm}
\SetKw{True}{true}
\SetKw{False}{false}
\KwIn{$G = (V, E)$, $c : V \rightarrow \N$, $k$}
\KwOut{$M$}
$M \leftarrow \emptyset$								\\
\Repeat{done}{
\label{line:outerloop}
 	$done \leftarrow{}$ \True							\\
 	\For{$M' \in M : |M'| \leq Ck$}{
 		\For{$V' \in V \setminus M : |V'| = |M'| + 1$}{
			\If{$M \setminus M' \cup V'$ is feasible}{
				$M \leftarrow{} M \setminus M' \cup V'$	\\
				$done \leftarrow{}$ \False				\\
			}
		}
 	}
}
\Return{$M$}

@@

We claim that the local search algorithm halts in polynomial time.
Observed that in every iteration the algorithm either improves the value of the solution
by one or otherwise it terminates. 
Thus, after a maximum of $n$ iterations the algorithm stops.
In every iteration we examine all the subsets of edges of a fixed size and test for feasibility,
both these operations can be done in polynomial time - $O(n^{Ck + 1})$.

To analyze the approximation ratio achieved by the local search algorithm consider an 
arbitrary but fixed optimal matching $M^* = \{s_1, \ldots, s_m\}$,
where $s_1, \ldots, s_m$ are the stars induced by the optimal solution.
Given the solution outputted by the local search algorithm,
we build the \emph{conflict graph} of the two solutions in which each node
represents a star from the optimal solution and edges exits between two nodes if
the local search solution has at least one edge that connects two stars, formally 
$G_\text{conflict} = (V, E)$ 
where $\{v_i : s_i \in M^* \}$ 
and $E = \{(v_i, v_j) : \exists (u,v) \in M \land u \in s_i, v \in s_j \}$.
Figure~\ref{fig:conflict} depicts this concept.
Denote by $d^*_i$ the sum of the vertex degree of the optimal solution in $s_i$, 
and by $d_i$ the sum of the vertex degree of the local search solution in $s_i$.

@@

>>>>

In this section we consider the unweighted variants of the problem.
We describe and analyze a local search algorithm, 
and show that when the maximum possible capacity, $C$, is fixed, the algorithm achieves 
a $\frac{C + 1}{2C} - \varepsilon$ 
approximation ratio for any $\varepsilon > 0$.
Throughout this section we consider $C$ to be fixed, and $k$ to be a fixed parameter.

@@

\begin{algorithm}
\SetKw{True}{true}
\SetKw{False}{false}
\KwIn{$G = (V, A)$, $c : V \rightarrow \N$, $k$}
\KwOut{$M$}
$M \leftarrow \emptyset$								\\
\Repeat{done}{
\label{line:outerloop}
 	$done \leftarrow{}$ \True							\\
 	\For{$M' \in M : |M'| \leq k$}{
 		\For{$A' \in A \setminus M : |A'| = |M'| + 1$}{
			\If{$M \setminus M' \cup A'$ is feasible}{
				$M \leftarrow{} M \setminus M' \cup A'$	\\
				$done \leftarrow{}$ \False				\\
			}
		}
 	}
}
\Return{$M$}

@@

We claim that the local search algorithm halts in polynomial time.
Observed that in every iteration the algorithm either improves the value of the solution
by one or otherwise it terminates. 
Thus, after a maximum of $n$ iterations the algorithm stops.
In every iteration we examine all the subsets of edges of a fixed size and test for feasibility,
both these operations can be done in polynomial time - $O(n^{k + 1})$.

To analyze the approximation ratio achieved by the local search algorithm consider an 
arbitrary but fixed optimal matching $M^* = \{s_1, \ldots, s_m\}$,
where $s_1, \ldots, s_m$ are the stars induced by the optimal solution.
Given the solution outputted by the local search algorithm,
we build the \emph{conflict graph} of the two solutions in which each node
represents a star from the optimal solution and edges exits between two nodes if
the local search solution has at least one edge that connects two stars, formally 
$G_\text{conflict} = (V, E)$ 
where $\{v_i : s_i \in M^* \}$ 
and $E = \{(v_i, v_j) : \exists (u,v) \in M \land u \in s_i, v \in s_j \}$.
Figure~\ref{fig:conflict} depicts this concept.
Denote by $d^*_i$ the sum of the vertex degree of the optimal solution in $s_i$, 
and by $d_i$ the sum of the vertex degree of the local search solution in $s_i$.
\todo{define this well}

@@

\todo{can I state the observation for any component of size at most (least)
$s$ ?? or does it have to be exavtly of size $s$ ?}
\begin{observation}
Let $U = \{v_1 \ldots v_s\}$ be the vertices of any connected component in
$G^{M^*}_M$ then $\frac{w(U)}{w^*(U)}$
\end{observation}
